Combinatorics of the geometry of Wilson loop diagrams

### 2019-01-04 General WLD combinatorics.tex
Some general tweaks to 2.3

We begin by proving some useful facts about flats of matroids associated to admissible Wilson loop diagrams.

@@

\begin{cor} \label{classifyflats}
If $F$ is a flat of a Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent flat. \end{cor}

In particular, any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.

%Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or cotractions of the associated matroids.

>>>>

We begin by proving some useful facts about propagator flats, and flats of matroids associated to admissible Wilson loop diagrams more generally.

@@

\begin{cor} \label{classifyflats}
If $F$ is a flat of a Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set and the set of non-supportive vertices. \end{cor}

In particular, any propagator flat can be written as a union of a cyclic propagator flat, an independent set and $F(\emptyset)$ for the appropriate Wilson loop diagram.

Next we examine properties of propagator flats associated to the complement of Wilson Loop diagrams.
%Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or cotractions of the associated matroids.
